A Causal Model of \hbox{DBMS} Suboptimality\\

### 2017-02-17 subopt-tods16/paper.tex
Sabah's updates

\todo{Sabah: redo hypotheses in these tables, for example, H1 doesn't go to
  subopt, then add the confirmatory numbers after we discuss them}
\begin{table}[t]
\tbl{Testing Hypotheses 1--7: Correlations on the Confiratory Study\label{tab:hyptest}}{%
%\begin{center}
\resizebox{85mm}{!}{
\begin{tabular}{c|c|c|c|c}
{\em Variable}& {\em Suboptimality}&{\em Repeats}&{\em CEPS} & {\em Discontinuity}\\
\hline
Operators in \hbox{DBMS} & ---&  {\bf H1a:}$-$0.16 & {\bf H1b:} & {\bf H1c:} \\
Correlation names & {\bf }  & {\bf H2a:} 0.54 & {\bf H2b:}  &{\bf H2c:} 0.49\\
Skew & {\bf H3:}  & --- & ---  & ---\\
Presence of aggregate & & {\bf H2d:}  & {\bf H2e:}  & {\bf H2f:} \\
Presence of primary key & & {\bf H2g:}  & {\bf H2h:}  & {\bf H2i:} \\
Presence of subquery & & {\bf H2j:}  & {\bf H2k:}  & {\bf H2l:} \\
Repeats& {\bf H7a:}  & --- & {\bf H6:}  & ---\\
CEPS &  {\bf H7b:} 0. & --- &  --- &{\bf H4:}  \\
Discontinuity & {\bf H7c:} 0.31 & --- & --- & ---\\
\end{tabular}
}
%\end{center}
}
\end{table}

\begin{table}[t]
\tbl{Testing Hypothesis 5: Interaction Strength on the Confirmatory Study\label{tab:hyptest8}}{%
%\begin{center}
\resizebox{85mm}{!}{
\begin{tabular}{c|c|c|c|c|c|c}
{\em Variable}& \multicolumn{2}{|c|}{{\em Repeats}}&\multicolumn{2}{|c|}{{\em CEPS}} & \multicolumn{2}{|c}{{\em Discontinuity}}\\
%\hline
{\em }&{Not SI\em }&{SI\em }&{Not SI\em }&{SI\em }&{Not SI\em }&{SI\em }\\
%&{\em }&{\em }&{\em }&{\em }\\
\hline
Correlation names &  & 0. &0. &0.  & 0. & 0. \\
Presence of aggregate  & 0. & 0. & 0. & 0. & 0. & 0. \\
Presence of primary key  &  & 0. & --- & --- & --- & --- \\
Presence of subquery  &  & 0. & --- & ---  & --- & --- 
\end{tabular}
}
%\end{center}
}
\end{table}

>>>>

\todo{Sabah: redo hypotheses in these tables, for example, H1 doesn't go to
  subopt, then add the confirmatory numbers after we discuss them}
\begin{table}[t]
\tbl{Testing Hypotheses 1--7: Correlations on the Confiratory Study\label{tab:hyptest}}{%
%\begin{center}
\resizebox{85mm}{!}{
\begin{tabular}{c|c|c|c|c}
{\em Variable}& {\em Suboptimality}&{\em Repeats}&{\em CEPS} & {\em Discontinuity}\\
\hline
Operators in \hbox{DBMS} & ---&  {\bf H1a:}$-$0.16 & {\bf H1b:} & {\bf H1c:} \\
Correlation names & {\bf }  & {\bf H2a:} 0.54 & {\bf H2b:}  &{\bf H2c:} 0.49\\
Skew & {\bf H3:}  & --- & ---  & ---\\
Presence of aggregate & & {\bf H2d:}  & {\bf H2e:}  & {\bf H2f:} \\
Presence of primary key & & {\bf H2g:}  & {\bf H2h:}  & {\bf H2i:} \\
Presence of subquery & & {\bf H2j:}  & {\bf H2k:}  & {\bf H2l:} \\
Repeats& {\bf H7a:}  & --- & {\bf H5:}  & ---\\
CEPS &  {\bf H7b:} 0. & --- &  --- &{\bf H4:}  \\
Discontinuity & {\bf H7c:} 0.31 & --- & --- & ---\\
\end{tabular}
}
%\end{center}
}
\end{table}

\begin{table}[t]
\tbl{Testing Hypothesis 6: Interaction Strength on the Confirmatory Study\label{tab:hyptest8}}{%
%\begin{center}
\resizebox{85mm}{!}{
\begin{tabular}{c|c|c|c|c|c|c}
{\em Variable}& \multicolumn{2}{|c|}{{\em Repeats}}&\multicolumn{2}{|c|}{{\em CEPS}} & \multicolumn{2}{|c}{{\em Discontinuity}}\\
%\hline
{\em }&{Not SI\em }&{SI\em }&{Not SI\em }&{SI\em }&{Not SI\em }&{SI\em }\\
%&{\em }&{\em }&{\em }&{\em }\\
\hline
Correlation names &  & 0. &0. &0.  & 0. & 0. \\
Presence of aggregate  & 0. & 0. & 0. & 0. & 0. & 0. \\
Presence of primary key  &  & 0. & --- & --- & --- & --- \\
Presence of subquery  &  & 0. & --- & ---  & --- & --- 
\end{tabular}
}
%\end{center}
}
\end{table}
